### 2019-10-07 190904_Paper_Thesis/Conclusion.tex
paper_thesis:v0

\label{chp:Conclusions}
\section{Conclusions}
...

\section{Future Works}
...
\begin{enumerate}
	\setlength{\itemsep}{1pt}
	\item Recognizing the in-air signature written along non-LOS. 
	\item Repeating the same data acquisition experiments in a different place
	\item Studying identification performances when multiple people are staying in the same room.
	\item To secure a reliable identification system, spoofing attack scenario should be investigated. 
\end{enumerate}

>>>>

\label{chp:Conclusions}
\section{Conclusions}
In this paper, we proposed a system for identity verification from Wi-Fi in-air signature signals based on triplet network. Three-channel ConvNet structures was adopted in order to learn discriminative features from the in-air signatures. Moreover, we proposed a input triplet mining approach based on the kernel and range space learning to faster the convergence speed.
Our experimental results on in-house Wi-Fi handwritten signature dataset showed the proposed network outperforms handcraft methods and Siamese network by improved verification accuracy and faster loss convergence.
\iffalse
\section{Future Works}
\begin{enumerate}
	\setlength{\itemsep}{1pt}
	\item Recognizing the in-air signature written along non-LOS. 
	\item Repeating the same data acquisition experiments in a different place
	\item Studying identification performances when multiple people are staying in the same room.
	\item To secure a reliable identification system, spoofing attack scenario should be investigated. 
\end{enumerate} 
\fi

### 2019-10-07 190904_Paper_Thesis/Introduction.tex
paper_thesis:v0

%\newpage
\newpage
\section{Motivation and Contributions}
The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
\item Adopted the kernel and the range (KAR) space learning to mine the distinctive triplet inputs which boost the convergence speed of the training loss in the triplet network.
\item Provision of an experimental study using an in-house Wi-Fi handwritten signature dataset collected from 50 subjects.
\end{itemize}

\section{Organization of Thesis}
The paper is organized as follows: related works including the triplet network and KAR space learning are introduced in Section 2 for immediate reference. Our proposed method is discussed in Section 3. Section 4 describes our experimental results and analysis. Some concluding remarks are given in Section 5.

>>>>

%\newpage
\newpage
\section{Motivation and Contributions}
The main contributions of our work can be summarized as follows:
\begin{itemize}
\item A system to utilize Wi-Fi handwritten signature signals for identity verification is proposed. We used the deep triplet network to obtain the discriminative features in limited training dataset.
\item In training of the triplet network, we propose hard triplet mining strategy using the kernel and range (KAR) space learning to faster the convergence speed.
\item We propose an experimental study using an in-house Wi-Fi handwritten signature dataset collected from 98 subjects.
\end{itemize}

\section{Organization of Thesis}
The rest of this paper is organized as follows: Section 2 introduces the triplet network and the Kernel and Range space learning. Our proposed system is described in Section 3. In Section 4, experimental results is discussed. Conclusions and future works  are presented in Section 5.

### 2019-10-07 190904_Paper_Thesis/abstract.tex
paper_thesis:v0

{
	\begin{flushright}
		Han-Cheol Moon\\
		School of Electrical and Electronic Engineering\\
		The Graduate School\\
		Yonsei University
	\end{flushright}
}
\vspace{0.1em}

...

\vspace{\stretch{1}}
\noindent
\hrulefill\\
{\bf Key words : Biometrics, Identification, In-Air Signature, Channel State Information, and
	Wi-Fi}
\parbox[t]{0.8\textwidth}
{}

>>>>

{
	\begin{flushright}
		Young-Woong Kwon\\
		School of Electrical and Electronic Engineering\\
		The Graduate School\\
		Yonsei University
	\end{flushright}
}
\vspace{0.1em}

Identity verification using Wi-Fi in-air handwritten signature is a challenge task in signature verification since the shape of the signal varies according to the direction in which the signature is written.
By using the handcraft features, it was difficult to verify identity from signatures entered in various directions. Moreover, the limited size of dataset also limited the training of deep learning models.
In this paper, we propose a system for identity verification from Wi-Fi in-air signature signals based on triplet network. Three-channel ConvNet structures is adopted in order to learn discriminative features from the in-air signatures. Moreover, we propose a input triplet mining approach based on the kernel and range space learning to faster the convergence speed.
Our experimental results on in-house Wi-Fi handwritten signature dataset shows the proposed network outperforms handcraft methods and Siamese network by improved verification accuracy and faster loss convergence.

\vspace{\stretch{1}}
\noindent
\hrulefill\\
{\bf Key words : Biometrics, In-air handwritten signature verification, Wi-Fi Channel State Information, triplet network and the Kernel and Range space learning}
\parbox[t]{0.8\textwidth}
{}
